Interactive Visual Analysis of Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-12-08 Rebuttal.md

Rebuttal
========

This rebuttal is written in markdown.

Reviewer 1
----------

- Figure 1 was completely removed since it does not supports the train of thought as we intended and due to lack of space
- Applicability: Comparison to standard workflow is not possible. The classic epidemiological workflow is strictly hypothesis driven and therefore requires a small set of 2 - 3 variables, which are correlated with a target variable. IVA methods amplify *hypothesis generation* and therefore aim to provide insight into unexpected relationships in the data.
- Exploration process is unclear
	- at the beginning of Section 5 - Experiments and Preliminary Results, all subjects

### 2014-12-08 draft.tex
minor revisions at draft and added comments to the Rebuttal

\cite{Klemm2013VMV} analyzed the lumbar spine variability of 490 \texttt{SHIP-2} subjects.

@@

They incorporate hierarchical agglomerative clustering to derive shape groups, yielding several groups of average shape and several outlier clusters.

@@

Our data extraction process is based on the detection algorithm and lumbar spine canal extraction presented by \cite{Klemm2013VMV}.

@@

\noindent Spine shape is influenced by several somatometric variables.

@@

As a first experiment we correlated the shape variable with the dichotomous back pain indicator using a \texttt{GPLOM}.

>>>>

% TODO: [high] This is currently only one paper!
In a prior work, we analyzed the lumbar spine variability of 490 \texttt{SHIP-2} subjects \cite{Klemm2013VMV}.

@@

We incorporate hierarchical agglomerative clustering to derive shape groups, yielding several groups of average shape and several outlier clusters.

@@

We use the same detection algorithm and lumbar spine canal extraction as foundation of this work.
%Our data extraction process is based on the detection algorithm and lumbar spine canal extraction presented by \cite{Klemm2013VMV}.

@@

%The first step is to analyze if the dichotomous back pain variable can be discriminated using single shape variables or sets of shape variables.
\noindent In this section, the image-derived variables are analyzed towards the dichotomous \emph{back pain} indicator using a \texttt{GPLOM} and all non-image variables using heterogenous correlations.
%In this section, we aim to retrieve correlations between the dichotomous \emph{back pain} indicator and the image-derived variables using a \texttt{GPLOM} as well as a assessment, which non-image variables 
Spine shape is influenced by several somatometric variables.

@@

As first experiment we correlated the shape variable with the dichotomous back pain indicator using a \texttt{GPLOM}.
